---
title: "simpleRegress"
author: "Teresa Juan"
date: "06/15/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

 
## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).
```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

as we compare LENGHT and WEIGHT to the first model of LENGHT and NECK, Adjusted R-squared gave us a small number of 0.7423 and Residual standard error of 5.432. comparing these two model Adjusted R-squre was better on first model LENGHT and NECK size, making these model not better.

```{r}
simp <- lm(CHEST~NECK,data=bears)
plot(CHEST~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
as we compare CHEST and NECK to the first model of LENGHT and NECK, Adjusted R-squared gave us a good number of 0.8714 and Residual standard error of 3.353. comparing these two model Adjusted R-squre was better on the CHEST and NECK size, making this model not better.

```{r}
simp <- lm(HEADWTH~NECK,data=bears)
plot(HEADWTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

As i compare HEADWTH~NECK to the first model of LENGTH and NECK
Adjusted R-square gave us a small number of 0.664 with a Residual Standard error of 0.8765. comparing this two the first model LENGHT and NECK is better because the Adjusted R-square was bigger  of 0.7476 and the residual standard error of 5.376 was small. making this model HEADWTH~NECK not better.


```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

when comparing LENGTH~HEADLEN with the first model of LENGTH~NECK Adjusted R-square gave us a larger number of 0.8434 and a small Residual standard error of 4.235 making this a better prediction then the on on model 1 where we compare LENGTH~NECK.

```{r}
simp <- lm(LENGTH~MONTH,data=bears)
plot(LENGTH~MONTH,data=bears)
abline(simp)
summary.lm(simp)
```

as we compare LENGTH ~ MONTH we get a Adjusted R-squared of -0.01153 and Residual standard error of 10.76. comparing these model to the first mode of LENGTH ~ NECK, the results were better in the first model, making it this a bad model.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```
As i compare LENGTH ~ AGE to the first model of LENGTH and NECK
Adjusted R-square gave us a small number of 0.5073 with a Residual Standard error of 7.511. comparing this two the first model LENGHT and NECK is better because the Adjusted R-square was bigger  of 0.7476 and the residual standard error of 5.376 was small. making this model HEADWTH~NECK not better. This model was on of the worst ones in all because it gave us a really big Adjusted R-squared number, and a small Adjusted R-squared number.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

By comparing LENGTH ~ HEADWTH with the first model LENGTH ~ NECK, it seems that this model is not better then the other because it gave us a Residual standard error of 0.5409 and Adjusted R-squared of 0.5321. It gave us a small Adjusted R-squared and a really hight Residual standard error. making it the wort model.

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```
As we predict LENGTH ~ CHEST with the firts model LENGTH ~ NECK, we can see that this model LENGTH ~ CHEST is better because it gave us a biger number on the Adjusted R-squared of 0.7869 and Residual standard error of  4.939. Adjusted R-squared number was bigger to predict LENGTH ~ CHEST then to predict LENGTH ~ NECK, and the Residual standard error was smaler then to predict LENGTH ~ NECK.

