---
title: "simpleRegress"
author: "Teresa Juan"
date: "06/15/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

 
## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).
```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

as we compare LENGHT and WEIGHT to the first model of LENGHT and NECK, Adjusted R-squared gave us a small number of 0.7423 and Residual standard error of 5.432. comparing these two model Adjusted R-squre was better on first model LENGHT and NECK size.

```{r}
simp <- lm(CHEST~NECK,data=bears)
plot(CHEST~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


```{r}
simp <- lm(HEADWTH~NECK,data=bears)
plot(HEADWTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```